Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues

### 2016-04-06 milestone1/paper/paper.tex
report

% first the title is needed
\title{Data- and Systems Paper: your title here}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Names}
%
\authorrunning{Put your names here}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\url{first@email.nl} \and \url{second@email.nl}}

@@

\subsection{Theaters Dataset}
% TODO describe theaters dataset (fields, contained data, semantics)

>>>>

% first the title is needed
\title{Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea. }
%
\authorrunning{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea.}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\url{first@vu.nl} \and \url{second@vu.nl}}

@@

\subsection{Theaters Dataset}
% TODO describe theaters dataset (fields, contained data, semantics)
The theaters dataset contains the following fields:

\begin{center}
	\begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
		\hline
		\textbf{Trcid} & \textbf{Title} & \textbf{Shortdescription} & \textbf{Longdescription} & \textbf{Calendarsummary} & \textbf{TitleEN} & \textbf{ShortdescriptionEN} & \textbf{LongdescriptionEN} & \textbf{CalendarsummaryEN } & \textbf{Types} & \textbf{Ids} & \textbf{Locatienaam} & \textbf{City} & \textbf{Adres} & \textbf{Zipcode} & \textbf{Latitude } & \textbf{Latitude} & \textbf{Urls} & \textbf{Media} & \textbf{Thumbnail} & \textbf{Datepattern\_startdate} & \textbf{Datepattern\_enddate} & \textbf{Singledates} & \textbf{Type1} & \textbf{Lastupdated} \\ \hline

		\hline
	\end{tabular}
\end{center}
